An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-29 paper.tex
Structure of the paper

We structure the remainder of this paper as follows.

%==================================================================================================
\section{Background and Datasets}

@@

Participants in the IETF must agree to abide by the policies and procedures
described at \url{https://www.ietf.org/about/note-well}, including the privacy
policy at \url{https://www.ietf.org/privacy-statement}. These make explicit
provision that mailing list archives and the metadata contained in the
Datatracker system will be made public, and it is this public data that
we process to extract the aggregate statistics presented in Sections
\ref{sec:trends-documents}, \ref{sec:trends-demographics}, \ref{sec:org-dynamics},
\ref{sec:behaviour} as well as the features analysed in Section
\ref{sec:success-factors}. We transfer and store data securely, and retain
it only for the time needed to perform the analysis.  Since we operate
entirely using the public APIs provided by IETF, we have no access to
private data about individuals.

@@

%==================================================================================================
\section{Understanding Participant Behaviour}
\label{sec:behaviour}

@@

%==================================================================================================
\section{Related Work}

@@

%==================================================================================================
\section{Conclusions}

>>>>

We structure the remainder of this paper as follows.
Section \ref{sec:background} introduces the IETF and the Internet Standards
development process, and reviews the data with which we work.
Section \ref{sec:trends-documents} considers trends in document production,
complexity, and correctness.
Section \ref{sec:trends-demographics} moves on to consider the people who
are involved in Internet standards development and how the demographics of
the community have shifted over time.
Section \ref{sec:org-dynamics} studies the interaction between participants,
explores who has influence and impact in the IETF and how that influence
is evident in their activities, and the dynamics of communications within
the IETF.
Section \ref{sec:language} considers communications within the IETF from
the perspective of language to explore whether there are differences in
linguistic patterns and language use in more influential participants,
and to consider how the use of language reflects the consensus-driven
nature of the standards development process.
Section \ref{sec:success-factors} then considers factors that lead to
success, exploring what makes a document likely to be completed and
used, and what makes a successful participant.
Finally, we review related work in Section \ref{sec:related} and conclude
in Section \ref{sec:conclusions}.

%==================================================================================================
\section{Background and Datasets}
\label{sec:background}

@@

Participants in the IETF must agree to abide by the policies and procedures
described at \url{https://www.ietf.org/about/note-well}, including the privacy
policy at \url{https://www.ietf.org/privacy-statement}. These make explicit
provision that mailing list archives and the metadata contained in the
Datatracker system will be made public, and it is this public data that
we process to extract the aggregate statistics presented in Sections
\ref{sec:trends-documents}, \ref{sec:trends-demographics}, \ref{sec:org-dynamics},
\ref{sec:language} as well as the features analysed in Section
\ref{sec:success-factors}. We transfer and store data securely, and retain
it only for the time needed to perform the analysis.  Since we operate
entirely using the public APIs provided by IETF, we have no access to
private data about individuals.

@@

%==================================================================================================
\section{Language and Influence}
\label{sec:language}

@@

%==================================================================================================
\section{Related Work}
\label{sec:related}

@@

%==================================================================================================
\section{Conclusions}
\label{sec:conclusions}
